### 2019-11-22 3_implementation.tex
More shrinking.

Spark~\cite{Spark10} is an implicitly-parallel programming model for
large scale data analytics.
The core abstractions in Spark are functional operators such as map,
reduce, and join. Data in Spark are stored in
\emph{resilient
  distributed datasets} (RDDs): globally-visible,
dynamically single-assignment data structures. Spark caches RDDs in memory to avoid unnecessary
disk traffic.

Spark has tasks internally but they are not exposed to the user,
so a Task Bench implementation must map the task graph to a set of operators that result in the
desired execution. We use
\lstinline[language=Scala]{flatMap} and
\lstinline[language=Scala]{groupByKey} to generate task
dependencies, and then \lstinline[language=Scala]{mapPartitions} to execute a
series of tasks. An explicit hash partitioner ensures that
Spark does not attempt to group multiple Task Bench tasks into a
single Spark task, as tasks in Task Bench already represent coarse-grained units of work.

@@

X10~\cite{X1005} is an explicitly parallel programming language for
place-based programming. The core features of X10 are \emph{places}
which represent distributed memories, a PGAS model where references to
remote objects can be held (but can only be dereferenced on the local
place), asynchronous tasks, and a place-changing construct to move the
execution of a task to a remote place. X10 also supports a variety of
synchronization primitives.

>>>>

Spark~\cite{Spark10} is an implicitly-parallel programming model for
data analytics.
The core abstractions in Spark are functional operators such as map,
reduce, and join. Data in Spark are stored in
\emph{resilient
  distributed datasets} (RDDs): globally-visible,
dynamically single-assignment data structures. Spark caches RDDs in memory to avoid unnecessary
disk traffic.

Spark has tasks internally but they are not exposed to the user,
so a Task Bench implementation must map the task graph to operators that result in the
desired execution. We use
\lstinline[language=Scala]{flatMap} and
\lstinline[language=Scala]{groupByKey} to generate
dependencies, and then \lstinline[language=Scala]{mapPartitions} to execute a
series of tasks. An explicit hash partitioner ensures that
Spark does not attempt to group multiple Task Bench tasks into a
single Spark task, as tasks in Task Bench already represent coarse-grained units of work.

@@

X10~\cite{X1005} is an explicitly parallel programming language for
place-based programming. Features include \emph{places}
which represent distributed memories, a PGAS model where references to
remote objects can be held (but can only be dereferenced on the local
place), asynchronous tasks, and a place-changing construct to move the
execution of a task to a remote place. X10 also supports a variety of
synchronization primitives.
